### 2023-12-12 latex/Plusone_configs/paper.tex
2011开始的回测config

\section*{Research Methodology}
\subsection*{VIX term structures decompositions}

% For figure citations, please use "Fig" instead of "Figure".
Nulla mi mi, Fig~\ref{fig1} venenatis sed ipsum varius, volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, \nameref{S1_Video} vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

@@

\subsection*{1. Trading signals constructions}
\subsection*{2. Proposed Machine Learning Algorithms}
\subsubsection*{2.1 XGBoost}
We first implement XGBoost machine learning algorithm to predict next-day returns of VIX CMFs, XGBoost is a scalable end-to-end tree boosting based on gradient tree boosting proposed by Freidman (1999). It shows promising results on various machine learning challenges. See XGBoost details in Chen and Guestrin (2016) work. Eq.1 presents the XGBoost algorithm implementation in our prediction task.

>>>>

\section*{Research Methodology}
\subsection*{VIX term structures decompositions}
The VIX is calculated by the Chicago Board Options Exchange (CBOE) and is based on the prices of options on the S&P 500 Index.
% For figure citations, please use "Fig" instead of "Figure".
Nulla mi mi, Fig~\ref{fig1} venenatis sed ipsum varius, volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, \nameref{S1_Video} vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

@@

\subsection*{1. Trading signals constructions}
Let $t$ denote time and let $VIX_t$ denote the value of VIX on that date. Let $d$ be an integer such that $d + 1$ is the number of VIX futures contracts, and let $T_1 < T_2 < • • • < T_(t+1)$ denote the
expiration dates of these VIX futures contracts. Let us denote:

\subsection*{2. Proposed Machine Learning Algorithms}
\subsubsection*{2.1 XGBoost}
We first implement XGBoost machine learning algorithm to predict next-day returns of VIX CMFs, XGBoost is a scalable end-to-end tree boosting based on gradient tree boosting proposed by Freidman (1999). It shows promising results on various machine learning challenges. See XGBoost details in Chen and Guestrin (2016) work. Eq.1 presents the XGBoost algorithm implementation in our prediction task.
